Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
Add sentence on tree runtimes

\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries are an order-of-magnitude faster than the baseline. We get another order-of-magnitude speedup when optimizing for performance.

>>>>

\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries, with runtimes ranging from \runtimetreelowzero{} to \runtimetreehighzero{}, are an
order-of-magnitude faster than the baseline, with runtimes ranging from
\runtimetreelowbase{} to \runtimetreehighbase{}. We get another order-of-magnitude speedup when
optimizing for performance, achieving runtimes as low as \runtimetreelowone{} to
\runtimetreehighone{}. These speedups, ranging widely from \lowxalphazero{}x to 
\highxalphaone{}x, depending on $\alpha$ and query, constitute significant workflow improvements
for the analyst.
